\begin{center}
\section*{\month}
\end{center}


\def\day{\textit{September 7st, 2021 Simon}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}

Yesterday I added a changing Recyclerviewer when you click a different folder.
At the beginning I hab big problems because the Recyclerviewer was called in the MainActivity
in the onCreate function wich was just called when you start the App so I couldn't use a boolean wich was set 
true when the fragments are called. So i figured out how I can call the Recyclerviewer from the Fragment. So every time 
the user clicks on a Folder an new Recyclerviewer is called and reads in the Data. I'm not sure if it reads in the Database every time. 
Maybe it just reads in the UI created by the ViewModel. Still the Programm uses a lot of Memory and it might be because of the 
different LiveDatas or the different observer because not idk how often the look for changes. Also i cant use a different Database read in function 
without wiping the Data from the Virtual machine

Today I added new Folders called Spam and Archive. They work the same way like the other Folders. 


\def\day{\textit{September 8st, 2021 Simon}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}

Today I managed to read the data from the eamailwriter into the Database
by starting the Intent in the messageCreateFragment and reading in the String from there. Adding them to these 
spezial Strings and calling these String with the data from the MainActivity. Sadly I still use the NewDraftActivity but idk why I have to.
Maybe somthing with the Intent or how the obActivityResult is called.
